---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# loadflux <img src='man/figures/logo.svg' align="right" height="139" />


<!-- badges: start -->
[![codecov](https://codecov.io/gh/atsyplenkov/loadflux/branch/master/graph/badge.svg?token=DI1DCJV15D)](https://codecov.io/gh/atsyplenkov/loadflux)
<!-- badges: end -->

The `loadflux` package is build for the comprehensive analysis of the intra-event suspended sediment dynamics.

## Installation

<!-- CRAN
You can install the released version of loadflux from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("loadflux")
```
 -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("atsyplenkov/loadflux")
```
## Example

This is a basic example which shows you how to split your series into hydrological events:

```{r example, message=FALSE, warning=FALSE}
library(dplyr)
library(loadflux)
data(djan)

df <- djan %>% 
  hydro_events(q = discharge,
               datetime = time,
               window = 21)

head(df)
```

### Plots

Then you can explore created hydrological events via `event_plot` function. This function creates an interactive [`dygraph`](https://rstudio.github.io/dygraphs/) object which is rendered as `html`.

```{r interactive_plot, message=FALSE, warning=FALSE, out.width = "50%", fig.align='center'}
library(dygraphs)

df %>%
  event_plot(q = SS, datetime = time, he = he)

```


And then plot the hysteresis loop by running `hysteresis_plot`

```{r hysteresis_plot, message=FALSE, warning=FALSE, out.width = "50%", fig.align='center'}
library(ggplot2)

df %>% 
  filter(he == 2) %>%
  hysteresis_plot(q = discharge,
                  ssc = SS,
                  base_font_size = 14)
```

### Hyseteresis indexes

This package also contains several function for hysteresis index calculation:

**Added**

- `SHI` - Simple Hystersis Index from [*Tsyplenkov et al., 2020*](https://link.springer.com/article/10.1007/s11368-020-02633-z)

**Pending**

- `HImid` - Hysteresis Index from [*Lawler et al., 2006*](https://www.sciencedirect.com/science/article/abs/pii/S0048969705005711)
- `HIaich` - Hysteresis Index from [*Aich et al., 2014*](https://www.sciencedirect.com/science/article/abs/pii/S0341816214001969)

To calculate a hysteresis index for your event run as follows:

```{r shi, message=FALSE, warning=FALSE}

df %>% 
  filter(he == 2) %>% 
  SHI(q = discharge,
      ssc = SS)

```

