---
title: "loadflux"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{loadflux}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Hydrological Events demarcation

This is a basic example which shows you how to split your series into hydrological events:

```{r example, message=FALSE, warning=FALSE}
library(dplyr)
library(loadflux)
data(djan)

df <- djan %>% 
  hydro_events(q = discharge, # Water discharge
               datetime = time, # POSISct argument
               window = 21) # Search window

head(df)
```

### Plots
Then you can explore visually hydrological events via `event_plot` function. This function creates an interactive [`dygraph`](https://rstudio.github.io/dygraphs/) object which is rendered as `html`. Every <span style="color:coral;">coral</span> stripe stands for one hydrological event.

```{r interactive_plot, message=FALSE, warning=FALSE, out.width = "90%", fig.align='center'}
library(dygraphs)

df %>%
  event_plot(q = discharge, # Y-axis
             datetime = time, #X-axis
             he = he) # Hydrological events

```

You can even explore both *Water Discharge* `Q` and *Suspended Sedimnet Concentration* `SSC` temporal variability:

```{r interactive_plot2, message=FALSE, warning=FALSE, out.width = "90%", fig.align='center'}
library(dygraphs)

df %>%
  event_plot(q = discharge, # Y-axis
             ssc = SS,
             datetime = time, #X-axis
             he = he) # Hydrological events

```
