---
title: "start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{R,echo=FALSE,results='hide',message=FALSE,include=FALSE, eval=TRUE}
if (!require(devtools))
  install.packages("devtools", repos = "http://cran.us.r-project.org")
if (!require(dplyr))
  install.packages("dplyr", repos = "http://cran.us.r-project.org"
  )
if (!require(zoo))
  install.packages("zoo", repos = "http://cran.us.r-project.org"
  )
```


The goal of overviewR is to make it easy to get an overview of a data set by displaying relevant sample information. At the moment, there are the following functions:

- `hydro_events` generates a tabular overview of the sample.  The general sample plots a two-column table that provides information on an id in the left column and a the time frame on the right column. 

The plots can be saved using the `ggsave()` command.

We present a short step-by-step guide as well as the functions in more detail below.

## Installation

A stable version of `loadflux` can be directly accessed on CRAN:
```{r, eval=FALSE}
install.packages("loadflux", force = TRUE)
```

To install the latest development version of `loadflux` directly from [GitHub](https://github.com/atsyplenkov/loadflux) use: 

```{r, message=FALSE, warning=FALSE, results = "hide", eval=FALSE}
library(devtools)
devtools::install_github("atsyplenkov/loadflux")
```

## Example

First, load the package.
```{r, include = FALSE, eval = FALSE}
install.packages("loadflux")
```

```{r, message=FALSE, warning=FALSE}
library(loadflux)
```

The following examples use a Djankuat river data set (`djan`) that comes with the package. This data contains direct water discharge and suspended sediment concentration measurements at Djankuat river (North Caucasus, Russia) in 2017.
