---
title: "Exploring turbidity fluctuations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{turbidity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is an example workflow of how to perform basic turbidity analysis with `loadflux` package and `tidyverse` ecosystem.

```{r setup, warning=FALSE, message=FALSE}
library(dplyr)
library(purrr)
library(tidyr)
library(tsibble)
library(loadflux)
```

### Hydrological Events
First, we need to demarcate hydrological events

```{r events, out.width = "90%", fig.align='center'}
data(djanturb)
df <- hydro_events(dataframe = djanturb,
                   q = discharge,
                   datetime = time,
                   window = 21)

df %>% 
  event_plot(q = discharge,
             datetime = time,
             he = he,
             ssc = ntu,
             y2label = "Turbidity")

```

### Turbidity Index
Then we can calculate Turbidity Index `TI` for every hydrological event

```{r ti_index}

TI_index <- df %>% 
  group_by(he) %>% 
  nest() %>% 
  mutate(TI = map_dbl(data, ~TI(.x, ntu, time))) %>% 
  select(-data) %>% 
  ungroup()

TI_index

```

### Hydrological events parameters

To summarize the hydrological events parameters an approach from `features` package can be used. For this purpose we need to transform our dataframe into `tsibble` object:

```{r to_tsibble}
library(tsibble)

df_ts <- df %>% 
  as_tsibble(key = he,
             index = time)

df_ts
```

Then we can calculate start, end and length of the every hydrological event:
```{r feat_ev}
library(feasts)

df_ts %>% 
  features(time,
           feat_event)

```

Or with the help of `brolgar` and `feasts` packages we can calculate turbidity statistics, autocorrelation and spectral functions:

```{r stats}
library(brolgar)
library(feasts)

df_ts %>% 
  features(ntu, feat_five_num)

df_ts %>% 
  features(ntu, c(feat_spectral,
                  feat_acf))

```

